\documentclass[a4paper, 12pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{fancyhdr}
\usepackage{amssymb}
\usepackage[margin=2cm]{geometry}
\usepackage{multicol}
% Define footer style
\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\renewcommand{\headrulewidth}{0pt} % Remove header rule
\renewcommand{\footrulewidth}{0.4pt} % Add a rule to the footer
\fancyfoot[C]{Trivandrum Maths and Computer Tuition - 9037030309, 04712723471}
\begin{document}
\begin{multicols}{2}	
	\section*{Multiple Choice Questions}
	Choose the correct answer from the given four options (1 to 20):
	
	
	
	\section*{Multiple Choice Questions}
	Choose the correct answer from the given four options (1 to 20):
	
	\begin{enumerate}
		\item Which of the following cannot be the probability of an event? 
		\begin{enumerate}
			\item 0.7
			\item $\frac{2}{3}$
			\item $-1.5$
			\item 15\%
		\end{enumerate}
		
		\item If the probability of an event is $p$, then the probability of its complementary event will be
		\begin{enumerate}
			\item $p - 1$
			\item $p$
			\item $1 - p$
			\item $1 - \frac{1}{p}$
		\end{enumerate}
		
		\item Out of one-digit prime numbers, one number is selected at random. The probability of selecting an even number is
		\begin{enumerate}
			\item $\frac{1}{2}$
			\item $\frac{1}{4}$
			\item $\frac{4}{9}$
			\item $\frac{2}{5}$
		\end{enumerate}
		
		\item When a die is thrown, the probability of getting an odd number less than 3 is
		\begin{enumerate}
			\item $\frac{1}{2}$
			\item $\frac{1}{3}$
			\item $\frac{1}{6}$
			\item 0
		\end{enumerate}
		
		\item A fair die is thrown once. The probability of getting an even prime number is
		\begin{enumerate}
			\item $\frac{1}{6}$
			\item $\frac{2}{3}$
			\item $\frac{1}{3}$
			\item $\frac{1}{2}$
		\end{enumerate}
		
		\item A fair die is thrown once. The probability of getting a composite number is
		\begin{enumerate}
			\item $\frac{1}{3}$
			\item $\frac{1}{6}$
			\item $\frac{2}{3}$
			\item 0
		\end{enumerate}
		
		\item If a fair die is rolled once, then the probability of getting an even number or a number greater than 4 is
		\begin{enumerate}
			\item $\frac{1}{2}$
			\item $\frac{1}{3}$
			\item $\frac{5}{6}$
			\item $\frac{2}{3}$
		\end{enumerate}
		
		\item If a letter is chosen at random from the letters of the English alphabet, then the probability that it is a letter of the word \textbf{DELHI} is
		\begin{enumerate}
			\item $\frac{1}{5}$
			\item $\frac{1}{26}$
			\item $\frac{5}{26}$
			\item $\frac{21}{26}$
		\end{enumerate}
		
		\item A card is selected at random from a pack of 52 cards. The probability of its being a red face card is
		\begin{enumerate}
			\item $\frac{3}{26}$
			\item $\frac{3}{13}$
			\item $\frac{2}{13}$
			\item $\frac{1}{2}$
		\end{enumerate}
	\end{enumerate}
	
	
	
	
	\begin{enumerate}
		\setcounter{enumi}{9}
		
		\item If a card is drawn from a well-shuffled pack of 52 playing cards, then the probability of this card being a king or a jack is
		\begin{enumerate}
			\item $\frac{1}{26}$
			\item $\frac{1}{13}$
			\item $\frac{2}{13}$
			\item $\frac{1}{4}$
		\end{enumerate}
		
		\item The probability that a non-leap year selected at random has 53 Sundays is
		\begin{enumerate}
			\item $\frac{1}{365}$
			\item $\frac{2}{365}$
			\item $\frac{2}{7}$
			\item $\frac{1}{7}$
		\end{enumerate}
		
		\item A bag contains 3 red balls, 5 white balls, and 7 black balls. The probability that a ball drawn from the bag at random will be neither red nor black is
		\begin{enumerate}
			\item $\frac{1}{5}$
			\item $\frac{1}{3}$
			\item $\frac{7}{15}$
			\item $\frac{8}{15}$
		\end{enumerate}
		
		\item A bag contains 4 red balls and 5 green balls. One ball is drawn at random from the bag. The probability of getting either a red ball or a green ball is
		\begin{enumerate}
			\item $\frac{4}{9}$
			\item $\frac{5}{9}$
			\item 0
			\item 1
		\end{enumerate}
		
		\item One ticket is drawn at random from a bag containing tickets numbered 1 to 40. The probability that the selected ticket has a number which is a multiple of 5 is
		\begin{enumerate}
			\item $\frac{1}{5}$
			\item $\frac{3}{5}$
			\item $\frac{4}{5}$
			\item $\frac{1}{3}$
		\end{enumerate}
		
		\item If a number is randomly chosen from the numbers 1, 2, 3, 4, $\ldots$, 25, then the probability of the number to be prime is
		\begin{enumerate}
			\item $\frac{7}{25}$
			\item $\frac{9}{25}$
			\item $\frac{11}{25}$
			\item $\frac{13}{25}$
		\end{enumerate}
		
		\item A box contains 90 cards numbered 1 to 90. If one card is drawn from the box at random, then the probability that the number on the card is a perfect square is
		\begin{enumerate}
			\item $\frac{1}{10}$
			\item $\frac{9}{100}$
			\item $\frac{1}{9}$
			\item $\frac{3}{100}$
		\end{enumerate}
		
		\item If a (fair) coin is tossed twice, then the probability of getting two heads is
		\begin{enumerate}
			\item $\frac{1}{4}$
			\item $\frac{1}{2}$
			\item $\frac{3}{4}$
			\item 0
		\end{enumerate}
		
		\item If two coins are tossed simultaneously, then the probability of getting at least one head is
		\begin{enumerate}
			\item $\frac{1}{4}$
			\item $\frac{1}{2}$
			\item $\frac{3}{4}$
			\item 1
		\end{enumerate}
		
		\item Lakshmi tosses two coins simultaneously. The probability that she gets at most one head is
		\begin{enumerate}
			\item 1
			\item $\frac{3}{4}$
			\item $\frac{1}{2}$
			\item $\frac{1}{7}$
		\end{enumerate}
		
		\item The probability of getting a bad egg in a lot of 400 eggs is 0.035. The number of bad eggs in the lot is
		\begin{enumerate}
			\item 7
			\item 14
			\item 20
			\item 21
		\end{enumerate}
		
	\end{enumerate}
	
	
	
	
	
	
	
	

	
	\section*{Section B}

	

	
	\textbf{1.} In a single throw of a die, find the probability of getting:
	\begin{enumerate}
		\item a number greater than 5
		\item an odd prime number
		\item a number which is a multiple of 3 or 4
	\end{enumerate}
	
	\textbf{2.} A lot consists of 48 mobile phones of which 42 are good, 3 have only minor defects, and 3 have major defects. Varnika will buy a phone if it is good, but the trader will only buy a mobile if it has no major defect. One phone is selected at random from the lot. What is the probability that it is:
	\begin{enumerate}
		\item acceptable to Varnika?
		\item acceptable to the trader?
	\end{enumerate}
	
	\textbf{3.} A bag contains 5 red, 8 white, and 7 black balls. A ball is drawn from the bag at random. Find the probability that the drawn ball is:
	\begin{enumerate}
		\item red or white
		\item not black
		\item neither white nor black
	\end{enumerate}
	
	\textbf{4.} A bag contains 5 white balls, 7 red balls, 4 black balls, and 2 blue balls. One ball is drawn at random from the bag. What is the probability that the ball drawn is:
	\begin{enumerate}
		\item white or blue
		\item red or black
		\item neither white nor black
	\end{enumerate}
	
	\textbf{5.} A box contains 20 balls bearing numbers 1, 2, 3, \dots, 20. A ball is drawn at random from the box. What is the probability that the number on the ball is:
	\begin{enumerate}
		\item an odd number
		\item divisible by 2 or 3
		\item not divisible by 10
	\end{enumerate}
	
	\textbf{6.} Find the probability that a number selected at random from the numbers 1, 2, 3, \dots, 35 is:
	\begin{enumerate}
		\item a prime number
		\item a multiple of 7
		\item a multiple of 3 or 5
	\end{enumerate}
	
	\textbf{7.} Cards marked with numbers 13, 14, 15, \dots, 60 are placed in a box and mixed thoroughly. One card is drawn at random from the box. Find the probability that the number on the card is:
	\begin{enumerate}
		\item divisible by 5
		\item a number which is a perfect square
	\end{enumerate}
	
	\textbf{8.} A box has cards numbered 14 to 99. Cards are mixed thoroughly and a card is drawn at random from the box. Find the probability that the card drawn from the box has:
	\begin{enumerate}
		\item an odd number
		\item a perfect square number
	\end{enumerate}
	
	\textbf{9.} A bag contains 5 red balls and some blue balls. If the probability of drawing a blue ball is four times that of a red ball, find the number of balls in the bag.
	
	\textbf{10.} A bag contains 18 balls out of which $x$ balls are white.
	\begin{enumerate}
		\item If one ball is drawn at random from the bag, what is the probability that it is a white ball?
		\item If 2 more white balls are put in the bag, the probability of drawing a white ball will be $\frac{9}{8}$ times that of the probability of drawing a white ball in part (i). Find the value of $x$.
	\end{enumerate}
\end{multicols}

\center{******************}	
\end{document}

	
	

	
	

	
	
	

