\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{textcomp}
\usepackage[a4paper, top=0.5cm, bottom=1.5cm, left=1.5cm, right=1.5cm]{geometry} % Minimize page padding

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\renewcommand{\headrulewidth}{0pt} % Remove header rule
\renewcommand{\footrulewidth}{0.4pt} % Add a rule to the footer
\fancyfoot[C]{Trivandrum Maths and Computer Tuition - 9037030309, 04712723471}

\begin{document}
	\begin{multicols}{2}
	\section*{  Class X ICSE - Section Formula}
	\section*{A. Multiple Choice Questions}
	
	\subsection*{Choose the correct option:}
	
	1. The centroid of the triangle whose vertices are $(-3, -7)$, $(-8, 6)$ and $(5, 10)$ is:
	\begin{enumerate}
		\item (0, 9)
		\item (0, 3)
		\item (1, 3)
		\item (3, 3)
	\end{enumerate}
	
	2. A line intersects the $y$-axis and $x$-axis at the points $A$ and $B$ respectively. If $(2, 5)$ is the mid-point of $AB$, then the coordinates of $A$ and $B$ are, respectively:
	\begin{enumerate}
		\item (0, 4) and $(-10, 0)$
		\item (0, 10) and $(-4, 0)$
		\item (0, 10) and (4, 0)
		\item (0, 4) and (10, 0)
	\end{enumerate}
	
	3. If $\left(\frac{a}{3}, 4\right)$ is the mid-point of a line segment joining the points $X(-6, 5)$ and $Y(-2, 3)$, then the value of $a$ is:
	\begin{enumerate}
		\item -4
		\item -6
		\item 12
		\item -12
	\end{enumerate}
	
	4. If the centroid of the triangle formed by $(7, x)$, $(y, -6)$ and $(9, 10)$ is $(6, 3)$, then the values of $x$ and $y$ respectively are:
	\begin{enumerate}
		\item 5, 3
		\item 5, 2
		\item -3, 2
		\item 6, 5
	\end{enumerate}
	
	5. The ratio in which the point $\left(\frac{3}{4}, \frac{5}{12}\right)$ divides the line segment joining the points $A\left(\frac{1}{2}, \frac{3}{2}\right)$ and $B(2, -5)$ is:
	\begin{enumerate}
		\item 1 : 2
		\item 3 : 2
		\item 1 : 5
		\item 2 : 3
	\end{enumerate}
	
	6. The fourth vertex $D$ of a parallelogram $ABCD$ whose three vertices are $A(-2, 3)$, $B(6, 7)$ and $C(8, 3)$ is:
	\begin{enumerate}
		\item (0, 1)
		\item (0, -1)
		\item (-1, 0)
		\item (1, 0)
	\end{enumerate}
	
	7. The ratio in which $P(4, m)$ divides the line segment joining the points $A(2, 3)$ and $B(6, -3)$ is:
	\begin{enumerate}
		\item 1 : 2
		\item 2 : 1
		\item 1 : 3
		\item 1 : 1
	\end{enumerate}
	
	8. If $\left(\frac{m}{2}, 5\right)$ is the mid-point of the line segment joining the points $Q(-6, 7)$ and $R(-2, 3)$, then the value of $m$ is:
	\begin{enumerate}
		\item -8
		\item 4
		\item 12
		\item -6
	\end{enumerate}
	
	9. The mid-point of the line segment joining the points $(-5, 7)$ and $(-1, 3)$ is:
	\begin{enumerate}
		\item (-3, 7)
		\item (-3, 5)
		\item (-1, 5)
		\item (5, -3)
	\end{enumerate}
	
	10. In the figure, $AB$ is a diameter of the circle with centre $O(4, 5)$. If $A$ is $(1, 1)$, then $B$ is:
	\begin{enumerate}
		\item (6, 9)
		\item (7, 9)
		\item (-7, 9)
		\item (7, -9)
	\end{enumerate}
	
	11. The ratio in which $P(4, m)$ divides the line segment joining the points $A(2, 3)$ and $B(6, -3)$ is:
	\begin{enumerate}
		\item 1 : 2
		\item 2 : 1
		\item 1 : 3
		\item 1 : 1
	\end{enumerate}
	
	12. If the mid-point of the line segment joining the points $P(6, a-2)$ and $Q(2, 3)$ is $(4, 1)$, then the value of $a$ is:
	\begin{enumerate}
		\item -5
		\item -6
		\item -7
		\item -8
	\end{enumerate}
	
	13. If the coordinates of one end of a diameter of a circle are $(2, 3)$ and the coordinates of its centre are $(-2, 5)$, then the coordinates of the other end of the diameter are:
	\begin{enumerate}
		\item (-6, 7)
		\item (6, -7)
		\item (6, 7)
		\item (-6, -7)
	\end{enumerate}
	
	14. The point which lies on the perpendicular bisector of the line segment joining points $A(-2, -5)$ and $B(2, 5)$ is:
	\begin{enumerate}
		\item (0, 0)
		\item (0, 2)
		\item (2, 0)
		\item (-2, 0)
	\end{enumerate}
	
	15. The vertices of a parallelogram in order are $A(1, 2)$, $B(4, y)$, $C(x, 6)$, $D(3, 6)$. The value of $x$ and $y$ respectively are:
	\begin{enumerate}
		\item 6, 2
		\item 3, 6
		\item 5, 6
		\item 1, 4
	\end{enumerate}
	
	16. A line intersects the $y$-axis and $x$-axis at the points $P$ and $Q$, respectively. If $(2, 5)$ is the mid-point of $PQ$, then the coordinates of $P$ and $Q$ respectively are:
	\begin{enumerate}
		\item (0, 5) and (-2, 0)
		\item (0, 10) and (-4, 0)
		\item (0, 4) and (-10, 0)
		\item (0, 10) and (4, 0)
	\end{enumerate}
	
	17. If $A(1, 3)$, $B(-1, 2)$, $C(2, 5)$ and $D(x, y)$ are the vertices of a parallelogram $ABCD$, then the value of $(x, y)$ is:
	\begin{enumerate}
		\item (3, 4)
		\item (4, 3)
		\item (0, 0)
		\item $\left(\frac{3}{2}, \frac{5}{2}\right)$
	\end{enumerate}
	
	\section*{B. Short Answer Type Questions}
	
	\begin{enumerate}
		\item Find the ratio in which the line segment joining $(-2, 5)$ and $(-5, -6)$ is divided by the line $y = -3$. Hence find the point of intersection.
		
		\item $P(1, -2)$ is a point on the line segment joining $A(3, -6)$ and $B(x, y)$ such that $AP : PB$ is equal to $2 : 3$. Find the coordinates of $B$.
		
		\item In what ratio is the line segment joining $P(5, 3)$ and $Q(-5, 3)$ divided by the $y$-axis? Also find the coordinates of the point of intersection.
		
		\item In what ratio does the point $C\left(\frac{3}{5}, \frac{11}{5}\right)$ divide the line segment joining the points $A(3, 5)$ and $B(-3, -2)$?
		
		\item Find the coordinates of the points of trisection (i.e., points dividing into three equal parts) of the line segment joining the points $A(2, -2)$ and $B(-7, 4)$.
		
		\item Find the ratio in which the $y$-axis divides the line segment joining the points $(5, 6)$ and $(-1, -4)$. Also, find the point of intersection.
		
		\item If the points $A(6, 1)$, $B(8, 2)$, $C(9, 4)$ and $D(p, 3)$ form a parallelogram, find the value of $p$.
		
		\item Prove that the points $(2, 1)$, $(8, 3)$, $(10, 4)$, $(4, 2)$ form a parallelogram.
		
		\item Find the length of the median of a triangle joining a vertex to the mid-point of its opposite side.
	\end{enumerate}
	
	\section*{C. Long Answer Type Questions}
	
	\begin{enumerate}
		\item Find the ratio in which the point $(-3, p)$ divides the line segment joining the points $(-5, -4)$ and $(-2, 3)$. Hence, find the value of $p$.
		
		\item If the coordinates of the midpoints of the sides of a triangle are $(1, 2)$, $(0, 1)$ and $(2, 1)$, find the coordinates of its vertices.
		
		\item The base $BC$ of an equilateral triangle $ABC$ lies on $y$-axis. The coordinates of point $C$ are $(0, 3)$. If the origin is the mid-point of the base $BC$, find the coordinates of the points $A$ and $B$.
		
		\item Find the area of the triangle whose vertices are $(0, 0)$, $(6, 0)$, and $(0, 8)$. Verify using the formula for the area of a triangle.
	\end{enumerate}
	
	\end{multicols}
	\center{******************}
	
\end{document}
